---
title: "Using scsuconn templates for reports and presentations by SCS at UCONN"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Usage}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "Usage_figures/"
)

ggplot2::theme_set(
  ggplot2::theme_classic()
)

```

`scsuconn` should be used when writing reports and presentations by SCS consultants at UCONN.

The below steps are recommended for successful workflow:

* install `scsuconn` usign `remotes::install_github('yuliasidi/scs_tmpl')`
* create a new project in `Rstudio` for your project
* create a new `Rmarkdown` doc using 'UConn - rmarkdown (pdf)' template



```{r setup}
library(scsuconn)
```


#Table examples:

See below some examples of tables, which could be useful for your project.
 
If you wish to print `data.frame` as is: 

```{r}
library(magrittr)

iris_sum <- iris%>%
  dplyr::group_by(Species)%>%
  dplyr::summarise_at(.vars = c('Sepal.Length', 'Sepal.Width'), 
                      .funs = c('mean', 'sd') )

knitr::kable(iris_sum, 
             caption = 'Sepal length/width mean/sd')
```


If you wish to print `data.frame` and control the decimals for all the variables
in the same way:
```{r}

knitr::kable(iris_sum, 
             caption = 'Sepal length/width mean/sd', digits = 2)
```

If you wish to print `data.frame` and control the decimals for each variable
separately:

```{r}
knitr::kable(iris_sum, 
             caption = 'Sepal length/width mean/sd', digits = c(0,1,1,3,3))

```

If you wish to print out a statsitical model:
```{r}
iris_setosa <- iris%>%
  dplyr::filter(Species == 'setosa')

model1 <- lm(Sepal.Length ~ Sepal.Width, iris_setosa)

knitr::kable(broom::tidy(model1), digits = c(0, 2, 3, 2, 4))
```


If you wish to print out models side-by-side comparison, if using pdf (default)
template, make sure to change `texreg::htmlreg` to `texreg::texreg` below:
```{r, results = 'asis'}

#option 5: Models summary side-by-side
model2 <- lm(Sepal.Length ~ Sepal.Width + Petal.Length, iris_setosa)
model3 <- lm(Sepal.Length ~ Sepal.Width + Petal.Length + Petal.Width, iris_setosa)

models <- list(model1, model2, model3)

texreg::htmlreg(models, caption = "Statistical models: coefficient estimates", 
               caption.above = TRUE)


```




#Figure examples:

By default all the figures will be saved under figures folder in your project.
The names of the figure output files can be specified in the chuck of the code as below

Below is an example of plotting a simple histogram. 

```{r sepwidth_hist}
library(ggplot2)

iris%>%
  ggplot(aes(x = Sepal.Width)) +
  geom_histogram(bins = 20, color = '#7C878E', fill = '#A4C8E1') +
  labs(x = "Sepal Width", y = 'Count', title = "Histogram example")
  
```


Below is an example of plotting a simple boxplot. 
```{r mpgcyl_box}

ggplot(mtcars, aes(x = as.factor(cyl), y = mpg)) + 
    geom_boxplot(fill = "#A4C8E1") + 
    labs(x = "Number of cylinders", y = 'Miles/(US) gallon', title = 'Boxplot example')

```


Below is an example of plotting a simple barplot. 
```{r mpgcyl_bar}

mtcars%>%
  dplyr::group_by(cyl)%>%
  dplyr::summarise(freq = n())%>%
  ggplot(aes(x = as.factor(cyl), y = freq)) + 
  geom_bar(stat = "identity", fill = "#A4C8E1") + 
  labs(x = "Number of cylinders", y = 'Count', title = 'Barplot example')

```

Below is an example of plotting a simple scatterplot. 
```{r iris_scatter}

ggplot(iris, aes(x = Sepal.Length, y = Sepal.Width, color=Species)) + 
    geom_point(size = 6) +
  labs(x = 'Sepal length', y = 'Sepal width', title = 'Scatterplot example') +
  theme(legend.position = 'bottom')
```

Below is an example of plotting a heatmap. 
```{r heat}
mydata <- mtcars[, c(1,3,4,5,6,7)]
cormat <- round(cor(mydata),2)

# Get lower triangle of the correlation matrix
  get_lower_tri<-function(cormat){
    cormat[upper.tri(cormat)] <- NA
    return(cormat)
  }
  # Get upper triangle of the correlation matrix
  get_upper_tri <- function(cormat){
    cormat[lower.tri(cormat)]<- NA
    return(cormat)
  }
  
upper_tri <- get_upper_tri(cormat)

melted_cormat <- reshape2::melt(upper_tri, na.rm = TRUE)

ggplot(data = melted_cormat, aes(Var2, Var1, fill = value)) +
  geom_tile(color = "white") +
  scale_fill_gradient2(low = "blue", high = "red", mid = "white", 
   midpoint = 0, limit = c(-1,1), space = "Lab", 
   name="Pearson\nCorrelation") +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, 
    size = 12, hjust = 1)) +
  coord_fixed() +
  labs(x = ' ', y = ' ', title = 'Heatmap example') 

```


[kableExtra Documentation](https://haozhu233.github.io/kableExtra/awesome_table_in_pdf.pdf)

[R graph gallery](https://www.r-graph-gallery.com/)