---
title: "Using scsuconn templates for reports and presentations by SCS at UCONN"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Usage}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "Usage_figures/"
)
```

`scsuconn` should be used when writing reports and presentations by SCS consultants at UCONN.

The below steps are recommended for successful workflow:

* install `scsuconn` usign `remotes::install_github('yuliasidi/scs_tmpl')`
* create a new project in `Rstudio` for your project
* create a new `Rmarkdown` doc using 'UConn - rmarkdown (pdf)' template



```{r setup}
library(scsuconn)
```


#Table examples:

See below some examples of tables, which could be useful for your project.
 
If you wish to print `data.frame` as is: 

```{r}
library(magrittr)

iris_sum <- iris%>%
  dplyr::group_by(Species)%>%
  dplyr::summarise_at(.vars = c('Sepal.Length', 'Sepal.Width'), 
                      .funs = c('mean', 'sd') )

knitr::kable(iris_sum, 
             caption = 'Sepal length/width mean/sd')
```


If you wish to print `data.frame` and control the decimals for all the variables
in the same way:
```{r}

knitr::kable(iris_sum, 
             caption = 'Sepal length/width mean/sd', digits = 2)
```

If you wish to print `data.frame` and control the decimals for each variable
separately:

```{r}
knitr::kable(iris_sum, 
             caption = 'Sepal length/width mean/sd', digits = c(0,1,1,3,3))

```

If you wish to print out a statsitical model:
```{r}
iris_setosa <- iris%>%
  dplyr::filter(Species == 'setosa')

model1 <- lm(Sepal.Length ~ Sepal.Width, iris_setosa)

knitr::kable(broom::tidy(model1), digits = c(0, 2, 3, 2, 4))
```


If you wish to print out models side-by-side comparison, if using pdf (default)
template, make sure to change `texreg::htmlreg` to `texreg::texreg` below:
```{r, results = 'asis'}

#option 5: Models summary side-by-side
model2 <- lm(Sepal.Length ~ Sepal.Width + Petal.Length, iris_setosa)
model3 <- lm(Sepal.Length ~ Sepal.Width + Petal.Length + Petal.Width, iris_setosa)

models <- list(model1, model2, model3)

texreg::htmlreg(models, caption = "Statistical models: coefficient estimates", 
               caption.above = TRUE)


```

#Figure examples:

By default all the figures will be saved under figures folder in your project.
The names of the figures can be specified in the chuck of the code as below
```{r abc}
plot(1:10,1:10)
```



[kableExtra Documentation](https://haozhu233.github.io/kableExtra/awesome_table_in_pdf.pdf)

[R graph gallery](https://www.r-graph-gallery.com/)